\subsection{Mount USB repository}

\begin{frame}[fragile]{Concept}
\begin{itemize}[<+->]
\item Somewhere there is a (git) repository...
\item and a !flying_start! directory
\item For now, this repository is simulated with an USB stick.
\item SW shall {\em not} depend on this USB simulation\\
      (except !procts/share000/comp/flying_start!)
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Windows (1/2)}
\begin{enumerate}
\item create directories !procts! and !procts_repo! next to each other,\\
      hence the path to !procts! is !<procts_path>!\\
      hence the path to !procts_repo! is !<procts_repo_path>!\\
\item open the windows command prompt
\item !diskpart!
\item !list volume!
\item Find in the list the volume which is labeled !PROCTS_REPO!,\\
    hence the volume number is !<v>!\\
    hence the letter !<l>!
\item !select volume <v>!
\item !assign mount="<procts_repo_path>"!
\seti % save enumeration counter
\end{enumerate}
\end{frame}

\begin{frame}[fragile]{Windows (2/2)}
\begin{enumerate}
\conti % continue with saved counter
\item !exit!
\item !xcopy <procts_repo_path>\flying_start\winx86r <procts_path>\flying_start\winx86r\!
\end{enumerate}
\end{frame}

\begin{frame}[fragile]{Linux}
\begin{enumerate}
\item \tbc
\end{enumerate}
\end{frame}

\begin{frame}[fragile]{OSX}
\begin{enumerate}
\item \tbc
\end{enumerate}
\end{frame}

\begin{frame}[fragile]{Flying start}
\begin{enumerate}
\item Navigate to !<procts_path>\flying_start\!
\item Execute \TOEXECUTE
\end{enumerate}
\end{frame}

\begin{frame}[fragile]{How to create the USB stick}
\begin{enumerate}
\item Obtain a removable mass storage device, e.g. USB stick
\item Format as FAT32 with label !PROCTS_REPO!
\item Unzip {\tbc} on this mass storage device in the root
\end{enumerate}
\end{frame}
